SunPy - Python for Solar Physics

### 2014-01-20 3-4-Helioviewer.tex
added in EPS images for helioviewer section

\subsection{Helioviewer}

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0, width=512, height=512)
\end{minted}
\caption{Acquisition of the latest AIA 304\AA\ image available at www.helioviewer.org.}
\label{code:downloadlatestpng}
\end{listing}

@@

The result is:

@@

@@

Example \ref{code:downloadjp2} demonstrates the querying, reading and
conversion of a Helioviewer JPEG2000 file into a SunPy Map object.
This functionality allows users to visualize and manipulate
Helioviewer-supplied image data in an identical fashion to a SunPy map
object generated from FITS data (see Section \ref{{}).

\begin{listing}
\begin{minted}{python}
filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO', instrument='HMI', detector='HMI', measurement='continuum')
from sunpy.map import Map
hmi = Map(filepath)
hmi.submap([200,550],[-400,-200]).peek()
\end{minted}
\caption{Acquisition and display of a Helioviewer JPEG2000 file.}
\label{code:downloadjp2}
\end{listing}

>>>>

\subsection{Helioviewer}\label{ssec:hv}

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0, width=512, height=512)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304.eps}
\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image available at
  www.helioviewer.org.}
\label{code:downloadlatestpng}
\end{listing}

@@

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 6, "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example.eps}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:downloadjp2}
\end{listing}

@@

Listing \ref{code:downloadjp2} demonstrates the querying, reading and
conversion of a Helioviewer JPEG2000 file into a SunPy Map object.
This functionality allows users to visualize and manipulate
Helioviewer-supplied image data in an identical fashion to a SunPy map
object generated from FITS data (see Section \ref{sec:maps}).

\begin{listing}
\begin{minted}{python}
filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO', instrument='HMI', detector='HMI', measurement='continuum')
from sunpy.map import Map
hmi = Map(filepath)
hmi.submap([200,550],[-400,-200]).peek()
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map.eps}
\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
  SunPy map object.}
\label{code:downloadjp2}
\end{listing}
